\documentclass{article}

\usepackage[letterpaper, margin=1in]{geometry}
\usepackage{setspace}


\title{SE 3XA3: Development Plan\\PyCards}

\author{Team 2, Team Name \\ \\ Aravi Premachandran premaa \\ Michael Lee leemr2 \\
Nikhil Patel patelna2 }

\date{}

\begin{document}

\maketitle


\section{Team Meeting Plan}

\noindent Team meetings are an essential part of the development process. It is
important that the members of this group approach this project in a structured
fashion and remain organized throughout. Meetings will be held during the latter
portion of the regularly scheduled lab sections (time permitting) or immediately
afterwards. In addition to the above listed times (or in lieu of in the case of
schedule conflicts), informal meetings shall be conducted via e-communication
using either of the Facebook and Skype platforms.\\Meetings will be scheduled on
a weekly basis to ensure there is no backlog of issues needing resolving, to
keep the project progressing on schedule, and as a general debrief on the past
week and for the coming week(s). Meetings will generally start with a review of
the past week(s) progress, including but not limited to deliverables completed
and deadlines met. Then any issues or concerns that have arisen or are ongoing
shall be raised by members of the group and addressed. Finally, meetings shall
conclude with a summary of progress, a reiteration of changes made and/or issues
resolved during the course of the meeting, and an overview of upcoming tasks and
deliverables.

\section{Team Communication Plan}

\noindent The primary means of communication for the members of this team shall
be through the instant messaging and conferencing services available using
Facebook and Skype. These platforms are both convenient and also free to use -
as such they are ideal for a project of this scale. Impersonal and routine
issues, comments, and conversation shall be done using Facebook. Any personal or
heavily involving issues or communications shall be done using Facebook if
satisfactory to all parties or using Skype if teleconferencing is deemed
necessary for efficient communication and resolution.

\section{Team member roles}

\noindent Leader: Nikhil Patel \newline
\noindent Experts:
\vspace{-2mm}
\begin{itemize}
	\itemsep0em
	\item Documentation: Aravi Premachandran
	\item Git: Nikhil Patel
	\item LaTeX: Michael Lee
\end{itemize}

\section{Git workflow plan} 

\noindent Our team will be implementing the Feature Branch Workflow using Git.
The reasoning behind using the feature branch workflow is that the master branch
should always contain stable, correct code. Development or modification of a new
or old feature will be done within a dedicated branch, and when completed a pull
request will be filed before merging with master. Using the feature branch
workflow isolates the development of features from the core codebase making it
easier for multiple members to work on the same or different features
simultaneously while keeping the most recent working version of the software
intact.


\section{Proof of Concept Demonstration Plan}

\noindent 

\section{Technology} 
\noindent The software product shall be redeveloped in the
same programming language as the existing implementation, Python 2.7.x . The IDE
of choice will be the simplistic IDLE editor though any execution of the
implementation shall be done using the command-line (shell). The pydoc
documentation tool will tentatively be used for document generation, and
pybuilder will tentatively be used both as a build tool and for testing.

\section{Coding Style} 

\noindent Python is a dynamic language in that variables are not bound to a
type, only the value(s) stored in it is. Python also poorly implements the
principle of least privilege. As such, it is especially important to follow a
consistent coding style in order to reduce the likelihood of making simple but
easy-to-miss errors such as type errors.

\section{Project Schedule} 

\noindent

point to Gantt Project chart

\end{document}
